---
title: "M.A._Data607_Assignment11"
author: "Muhammad Ahmad"
format: html
editor: visual
---

### Approach

  I choose to use a package that already exist to do content-based filtering.
The package I am using is the recommenderlab package authored by Michael Hahsler. I would like my algorithm to recommend the top 5 items based off different customer buyer history. I will test my algorithm using rank based metrics to see how accurate its based off the data. Some rank based metrics I will use include Precision, Recall, and F1-scores. 

### Challenges

  The challenges I think of now is if the data is missing information to make accurate recommendations and how to tackle that. The first fix I can think of is to recommend items that may be popular in the customers area. I am also worried that the system might overspecialize certain items based on a customers data. I experience this problem from my customer end application like YouTube when I only get recommended videos that I may have watch a lot of recently but got sick of. Using weights or some other method of random item generation recommendations may help diversify item recommendation. 


### Libraries
```{r}
library(dplyr)
library(recommenderlab)
library(tidyverse)
library(tidyr)
library(readxl)
library(caret)
```
### Dataset 

```{r}
url <- "https://raw.githubusercontent.com/MuhammadAhmad0006/Data607_Assignment11/refs/heads/main/MovieRatings.csv"


MovieRatingsRAW <- read.csv(url)
head(MovieRatingsRAW)
```


After reviewing this data set I believe the best personalized recommendation algorithm is user to user collaborative filtering. This is because of the focus of user rating input. 

```{r}
MovieRatings_df <- as.data.frame(MovieRatingsRAW)
row.names(MovieRatings_df) <- MovieRatings_df[,1]
MovieRatings_df <- MovieRatings_df[,-1]
MovieRatings_df
```

```{r}
MovieRatings_df[] <- lapply(MovieRatings_df, as.numeric)
ratings_matrix <- as.matrix(MovieRatings_df)
ratings <- as(ratings_matrix, "realRatingMatrix")
ratings
```


### Implementing User Based Collaborative Algorithm

```{r}
scheme <- evaluationScheme(ratings,
                           method = "cross-validation",
                           k = 3,
                           given = 1)
```

```{r}
model <- Recommender(getData(scheme, "train"),
                     method = "UBCF")
```

```{r}
pred <- predict(model,
                getData(scheme, "known"),
                type = "ratings")
```

```{r}
accuracy <- calcPredictionAccuracy(pred,
                                   getData(scheme, "unknown"))

accuracy

```

```{r}
final_model <- Recommender(ratings, method = "UBCF")

for(i in 1:nrow(ratings)){

  top3 <- predict(final_model, ratings[i], n = 3)
  rec_list <- as(top3, "list")

  if(length(rec_list[[1]]) > 0){

    cat("Top 3 Recommendations for", rownames(ratings_matrix)[i], ":\n")
    print(unlist(rec_list))
    break

  }

}

```


### Citations 

